---
title: "Report on  Science and Technology Research Institutes in Kerala"
output:
  word_document:
    reference_docx: style.docx
    number_sections: yes
date: '`r format(Sys.Date(),"%B %d, %Y")`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(devtools)
library(knitr)
library(epoxy)
source("code.R",local = knitr::knit_global())
```

This is the `r rmarkdown::metadata$title`. There are a total of `r nrow(df)` research institutions in Kerala. Of these, `r ntype[1]` are `r level_ntpe[1]` government owned and `r ntype[2]` `r if_else( ntype[2]<2,"is","are")` `r level_ntpe[2]` owned `r if_else(no_info==0,".",
        paste("while there was",no_info, 
              "organization about which information was not available. ")
)`Major sectors of research of these institutions are `r glue::glue_collapse(x = sectors[-length(sectors)], ", ", last = " and ")`.

Detailed information about the fields of research of these organizations are given below
```{r include=FALSE}
is_docx <- knitr::pandoc_to("docx")
is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'latex'
```

```{r ft.align="left",ft.split=T,echo=F,results='asis',warning=F,message=F,eval=is_docx}
library(flextable)
require("gdtools")
ft<-flextable(field_table)
ft<-autofit(ft)
ft<-theme_booktabs(ft)
ft<-flextable::set_caption(ft,"No of Organizations by Field of Research")
ft <- flextable::footnote(ft, i=14,j=1,
               value = as_paragraph("Some oganizations were under different names or the website was not functional"),
               ref_symbols = "*",
               part = "body",inline = )
ft<-fontsize(ft,size = 10,part = "all")
fontname<-"Times New Roman"
ft<-flextable::font(ft,fontname = fontname,part = "all")
ft
```
```{r tab1,eval=is_latex,echo=F,results='asis',fig.pos='!H',warning=F,message=F}
library(kableExtra)
field_table %>% kable(caption ="No of Organizations by Field of Research" ) %>% kable_styling(full_width = F,
                              latex_options = "hold_position") %>% 
  kable_classic()
```


```{glue mainchunk,eval=F}
# {institute}
{new_ins}  works under the aegis of {tolower(type)} government and works primarily in the {tolower(field)} sector. The primary research of the organization is on **{tolower(focus)}**.

- The institute has following research divisions to undertake research.  
  - {Research_Divisions}

- The organisation is equiped with following research infrastructure  
  - {stri_trans_totitle(RD_Infrastructure)}  

- The ongoing researches in the institute are     
  - {Ongoing_Researches}   

- The organisation has made commendable progress and below are few of their achievements  
  - {Achievements}

```

```{glue ref.label="mainchunk",data=df}

```

